Market simulator

### 2020-10-08 analysis/05_market_simulator.Rmd
Moved File Inputs to Import tab

# Organization file input
fileInput(
  "file_org",
  "Import Organization Data"
)

# Persona file input
fileInput(
  "file_per",
  "Import Persona Data"
)
```

@@

```{r import}
# Render the organization configurations as a table
renderTable({
  org_import = read_csv(input$file_org$datapath)

>>>>

@@

```{r import}
# Organization file input
fileInput(
  "file_org",
  "Import Organization Data"
)

# Persona file input
fileInput(
  "file_per",
  "Import Persona Data"
)

# Render the organization configurations as a table
renderTable({
  org_import = read_csv(input$file_org$datapath)
